Hierarchy Builder: algebraic~hierarchies made easy in Coq with Elpi

### 2020-04-25 hb.tex
color HB commands differently
fix

Definition Z_Ring_axioms : Ring_of_Monoid Z _ :=                        #\label{demo:theory:z:ring:axioms}#
  Ring_of_Monoid.Build Z 1 Z.opp Z.mul
    Z.add_opp_diag_l Z.add_opp_diag_r Z.mul_assoc Z.mul_1_l Z.mul_1_r
    Z.mul_add_distr_r Z.mul_add_distr_l.

>>>>

Definition Z_Ring_axioms : Ring_of_Monoid Z :=                        #\label{demo:theory:z:ring:axioms}#
  Ring_of_Monoid.Build Z 1 Z.opp Z.mul
    Z.add_opp_diag_l Z.add_opp_diag_r Z.mul_assoc Z.mul_1_l Z.mul_1_r
    Z.mul_add_distr_r Z.mul_add_distr_l.
